\documentclass{article}
\usepackage{enumitem}

\title{Deep Reinforcement Learning Concepts Project}
\author{B9AI105 REINFORCEMENT LEARNING}
\date{18/3/2024}

\begin{document}

\maketitle

\section*{Objective}
Develop a comprehensive understanding of key concepts in deep reinforcement learning (DRL) and algorithms used in DRL, with a practical implementation in the Frozen Lake environment.

\section*{Task}
Choose one of the following topics related to DRL:
\begin{enumerate}[label=\arabic*.]
    \item Deep Q-Network (DQN)
    \item Replay Buffer
    \item Target Network
    \item Double DQN
    \item Prioritized Experience Replay
    \item Advantage Function
    \item Long Short-Term Memory (LSTM) in Deep Recurrent Q-Networks (DRQN)
    \item Value-Based Methods
    \item Policy-Based Methods
    \item Policy Gradient Method
    \item Reward-to-Go
    \item Policy Gradient with Baseline Function
    \item Baseline Function
\end{enumerate}

\subsection*{Implementation Task}
\begin{itemize}
    \item Implement the chosen concept or algorithm in the Frozen Lake environment using OpenAI Gym.
    \item Train an agent to navigate the Frozen Lake using the implemented algorithm.
    \item Compare the performance of your agent with different hyperparameters and settings.
\end{itemize}

\section*{Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Write a detailed explanation of the chosen topic, covering the following aspects:
    \begin{itemize}
        \item Definition and purpose of the concept or algorithm.
        \item Why it is important or necessary in reinforcement learning.
        \item How it is used or implemented in DRL algorithms.
        \item Any advantages, disadvantages, or variations of the concept or algorithm.
    \end{itemize}
    \item Provide a code example or pseudocode illustrating the concept or algorithm in action in the Frozen Lake environment.
    \item Include references to academic papers, articles, or online resources that further explain the concept or algorithm.
\end{enumerate}

\section*{Deliverables}
\begin{itemize}
    \item A written report or presentation summarizing the chosen topic, including the explanation, code example (if applicable), and references.
    \item Code files for the implementation in the Frozen Lake environment.
\end{itemize}

\section*{Submission Guidelines}
\begin{itemize}
    \item Submit the report or presentation slides in PDF format.
    \item Include the code files in a separate folder or archive.
    \item Make sure to submit this assignment by \textbf{18th of April 2024}
\end{itemize}

\section*{Evaluation Criteria (Total: 100 points)}
\begin{enumerate}[label=\arabic*.]
    \item Explanation of Chosen Topic (30 points)
    \item Code Implementation (30 points)
    \item Performance Evaluation (20 points)
    \item Documentation (10 points)
    \item References and Further Reading (5 points)
    \item Overall Presentation (5 points)
\end{enumerate}

\end{document}
